---
title: "Presentation Title"
subtitle: "Subtitle or Course Name"
author: "Author Name"
institute: "University of Wisconsin–Madison"
date: today
date-format: "MMMM D, YYYY"

format:
  beamer:
    pdf-engine: xelatex
    include-in-header: _uw-beamer-preamble.tex

    # ── Layout ─────────────────────────────────────────────────
    aspectratio: 169          # 16:9 (use 43 for 4:3)
    fontsize: 11pt

    # ── Code highlighting ──────────────────────────────────────
    # 'tango' works well for light mode; 'zenburn' for dark.
    highlight-style: tango

    # ── Title page ─────────────────────────────────────────────
    # Tells Beamer to use the uwmadison title page template
    # defined in _uw-beamer-preamble.tex.
    template-partials:
      - title.tex           # see note at bottom of this file

execute:
  echo: false
  warning: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
source("../R/theme_uw.R")

# Match the plot theme to the preamble toggle:
#   \uwdarkfalse  → theme_uw()
#   \uwdarktrue   → theme_uw_dark()
theme_set(theme_uw(base_size = 9))   # small base size for Beamer
```

## Slide with bullet points

- First bullet point
- Second bullet point
  - Indented sub-point
- Third bullet point

\begin{uwbox}{Key concept}
Use the \texttt{uwbox} environment from the preamble for brand-styled
block highlights.
\end{uwbox}

## Slide with a figure

```{r}
#| label: fig-scatter
#| fig-cap: "Caption appears below the figure in the slide."
#| fig-width: 5.5
#| fig-height: 3.2
#| out-width: "90%"

ggplot(mpg, aes(x = displ, y = hwy, color = drv)) +
  geom_point(size = 1.8, alpha = 0.85) +
  scale_color_uw(labels = c("4-wheel", "Front", "Rear")) +
  labs(
    title = "Displacement vs. Highway MPG",
    x     = "Displacement (L)",
    y     = "Highway MPG",
    color = "Drive"
  )
```

## Slide with two columns

:::::: {.columns}

::: {.column width="48%"}

Some explanatory text on the left.

- Point A
- Point B  
- Point C

:::

::: {.column width="48%"}

```{r}
#| fig-width: 3.5
#| fig-height: 3

mpg |>
  count(class) |>
  ggplot(aes(x = n, y = reorder(class, n))) +
  geom_col(fill = uw_color("badger_red")) +
  labs(x = "Count", y = NULL)
```

:::

::::::

## Slide with a table

```{r}
library(knitr)

mpg |>
  group_by(drv) |>
  summarise(
    n        = n(),
    mean_hwy = round(mean(hwy), 1),
    mean_cty = round(mean(cty), 1)
  ) |>
  mutate(drv = recode(drv, `4` = "4-wheel", f = "Front", r = "Rear")) |>
  kable(
    col.names  = c("Drive", "n", "Hwy MPG", "City MPG"),
    booktabs   = TRUE,
    linesep    = ""
  )
```

## Incremental slide

Content appears item by item with Beamer pauses:

- First item \pause
- Second item \pause
- Third item

## {.plain}

\begin{center}
  {\Large\bfseries\color{BadgerRed} Thank You}\\[1em]
  {\normalsize Author Name}\\[0.3em]
  {\small Department · University of Wisconsin--Madison}\\[0.3em]
  {\small \texttt{author@wisc.edu}}
\end{center}

<!--
NOTE ON title.tex
─────────────────
The `template-partials: title.tex` line above tells Quarto to use
a custom title page partial. To use the UW title page template
defined in `_uw-beamer-preamble.tex` (\defbeamertemplate{title page}{uwmadison}),
create a minimal title.tex file in slides/ with:

  \setbeamertemplate{title page}[uwmadison]
  \maketitle

If you prefer Beamer's default title page, simply remove the
`template-partials` key from the YAML above.
-->
