---
title: "Presentation Title"
subtitle: "Subtitle or Course Name"
author: "Author Name"
institute: "University of Wisconsin–Madison"
date: today
date-format: "MMMM D, YYYY"

format:
  revealjs:
    # ── Theme ──────────────────────────────────────────────────
    # Light: white background, Badger Red headings
    theme: [default, _uw-light.scss]
    # Dark: near-black background, Badger Red accents
    # theme: [default, _uw-dark.scss]

    # ── Layout ─────────────────────────────────────────────────
    slide-number: c/t        # current/total
    progress: true
    width: 1280
    height: 720
    margin: 0.08

    # ── Code ───────────────────────────────────────────────────
    highlight-style: github  # swap to 'github-dark' with dark theme
    code-line-numbers: false

    # ── Navigation ─────────────────────────────────────────────
    controls: false
    hash: true
    history: true

execute:
  echo: false
  warning: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
source("../R/theme_uw.R")

# Use theme_uw() for light slides, theme_uw_dark() for dark slides.
# Set your plot theme once here so all chunks inherit it.
# Light theme (matches _uw-light.scss):
plot_theme <- theme_uw(base_size = 14)
# Dark theme (matches _uw-dark.scss — uncomment and swap scss above):
# plot_theme <- theme_uw_dark(base_size = 14)

theme_set(plot_theme)
```

## Slide with bullet points

- First bullet point
- Second bullet point
  - Indented sub-point
  - Another sub-point
- Third bullet point

## Slide with a figure

```{r}
#| label: fig-scatter
#| fig-cap: "Caption appears below the figure."
#| fig-width: 7
#| fig-height: 4.2

ggplot(mpg, aes(x = displ, y = hwy, color = drv)) +
  geom_point(size = 2.5, alpha = 0.85) +
  scale_color_uw(labels = c("4-wheel", "Front", "Rear")) +
  labs(
    title = "Engine Displacement vs. Highway MPG",
    x     = "Displacement (L)",
    y     = "Highway MPG",
    color = "Drive"
  )
```

## Slide with two columns {.columns-2}

:::: {.columns}

::: {.column width="48%"}

### Left column

Some explanatory text, a list, or another element.

- Point A
- Point B
- Point C

:::

::: {.column width="48%"}

```{r}
#| fig-width: 5
#| fig-height: 4

mpg |>
  count(class) |>
  ggplot(aes(x = n, y = reorder(class, n))) +
  geom_col(fill = uw_color("badger_red")) +
  labs(x = "Count", y = NULL)
```

:::

::::

## Slide with a callout box

Use a `.uw-box` div for brand-styled highlights:

::: {.uw-box}
**Key takeaway** — This box uses the Badger Red border defined in the SCSS theme. It is a good place for definitions, key results, or important caveats.
:::

Or use Quarto's built-in callout blocks:

::: {.callout-note}
Standard Quarto note callout.
:::

## Slide with a table

```{r}
#| label: tbl-summary

library(knitr)

mpg |>
  group_by(drv) |>
  summarise(
    n         = n(),
    mean_hwy  = round(mean(hwy), 1),
    mean_city = round(mean(cty), 1)
  ) |>
  mutate(drv = recode(drv, `4` = "4-wheel", f = "Front", r = "Rear")) |>
  kable(col.names = c("Drive", "n", "Mean Hwy MPG", "Mean City MPG"))
```

## Incremental reveal {.incremental}

Items appear one at a time:

- First revealed
- Then this one
- Finally this

## Slide with speaker notes

Main slide content goes here.

::: {.notes}
Speaker notes are hidden from the audience. Press **S** during
the presentation to open the speaker view. Notes can be as long
as needed — they won't affect the slide layout.
:::

## Section divider {background-color="#C5050C" color="white"}

::: {style="color: white; font-size: 1.6em; font-weight: bold;"}
Section Title
:::

::: {style="color: rgba(255,255,255,0.8); font-size: 0.85em;"}
Use `background-color="#C5050C"` on any slide for a Badger Red divider.
:::

## Thank you {background-color="#C5050C"}

::: {style="color: white; text-align: center;"}

**Author Name**

Department · University of Wisconsin–Madison

`author@wisc.edu`

:::
