---
title: "Getting Started with uwbranding"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with uwbranding}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  fig.width  = 6,
  fig.height = 3.5,
  out.width  = "100%"
)
```

The **uwbranding** package provides ggplot2 themes, color palettes, and Quarto
document templates that conform to the
[UW–Madison brand identity](https://brand.wisc.edu/).

```{r load}
library(uwbranding)
library(ggplot2)
library(dplyr)
```

> **Note on fonts.** The brand themes use Crimson Pro, Red Hat Display, and Red
> Hat Text. If these aren't installed as system fonts, ggplot2 will fall back to
> its default — the themes will still work, but typography won't match the brand.
> Download links are at <https://brand.wisc.edu/visual-identity/typography/>.

---

## Brand colors

All official colors are in the named vector `uw_colors`. Use `uw_color()` to
retrieve specific values by name.

```{r colors-vector}
uw_colors
```

```{r colors-lookup}
uw_color("badger_red")
uw_color("badger_red", "dark_red", "light_gray")
```

Here they are at a glance:

```{r colors-swatch, fig.height = 2.8, echo = FALSE}
swatch <- tibble::tibble(
  name  = factor(names(uw_colors), levels = names(uw_colors)),
  color = unname(uw_colors),
  group = c("Primary", "Primary", "Secondary", "Secondary", "Secondary",
            "Accent", "Accent", "Accent")
)

ggplot(swatch, aes(x = name, y = 1, fill = name)) +
  geom_tile(color = "white", linewidth = 1.5) +
  geom_text(aes(label = color), vjust = 3.2, size = 2.8,
            family = "Red Hat Text", color = "white",
            data = \(d) filter(d, name %in% c("badger_red", "dark_red",
                                               "black", "gray_blue", "blue"))) +
  geom_text(aes(label = color), vjust = 3.2, size = 2.8,
            family = "Red Hat Text", color = "#444444",
            data = \(d) filter(d, !name %in% c("badger_red", "dark_red",
                                                "black", "gray_blue", "blue"))) +
  scale_fill_manual(values = setNames(swatch$color, swatch$name),
                    guide  = "none") +
  facet_grid(. ~ group, scales = "free_x", space = "free") +
  theme_void() +
  theme(
    axis.text.x     = element_text(size = 8, margin = margin(t = 2)),
    strip.text      = element_text(face = "bold", size = 9, margin = margin(b = 4)),
    panel.spacing.x = unit(0.6, "lines"),
    plot.margin     = margin(4, 4, 4, 4)
  )
```

---

## Light theme

`theme_uw()` is the default theme for PDF documents and light-background slides.
It pairs Badger Red headings with a clean white panel.

```{r theme-uw-scatter}
ggplot(mpg, aes(x = displ, y = hwy, color = drv)) +
  geom_point(size = 2, alpha = 0.8) +
  scale_color_uw(labels = c("4-wheel", "Front", "Rear")) +
  labs(
    title    = "Engine Displacement vs. Highway MPG",
    subtitle = "Motor Trend Car Road Tests",
    x        = "Displacement (L)",
    y        = "Highway MPG",
    color    = "Drive",
    caption  = "Source: ggplot2::mpg"
  ) +
  theme_uw()
```

The `grid` argument controls which gridlines are shown (`"both"`, `"x"`, `"y"`,
`"none"`). For bar charts, `grid = "x"` is usually cleaner.

```{r theme-uw-bar, fig.height = 3.8}
mpg |>
  count(manufacturer) |>
  slice_max(n, n = 10) |>
  ggplot(aes(x = n, y = reorder(manufacturer, n))) +
  geom_col(fill = uw_color("badger_red")) +
  labs(title = "Top 10 Manufacturers", x = "Count", y = NULL) +
  theme_uw(grid = "x")
```

`title_color` accepts any color name from `uw_colors` or a raw hex string —
useful when Badger Red doesn't contrast enough against your content:

```{r theme-uw-title-color, fig.height = 2.2}
ggplot(mpg, aes(x = hwy)) +
  geom_histogram(fill = uw_color("dark_red"), bins = 20) +
  labs(title = "Highway MPG Distribution", x = "Highway MPG", y = "Count") +
  theme_uw(title_color = "black")
```

---

## Color scales

### Discrete (light)

`scale_color_uw()` and `scale_fill_uw()` apply [uw_palette_discrete] —
ordered for visibility on white:

```{r scales-discrete}
mpg |>
  count(manufacturer, drv) |>
  ggplot(aes(x = n, y = reorder(manufacturer, n), fill = drv)) +
  geom_col() +
  scale_fill_uw(labels = c("4-wheel", "Front", "Rear")) +
  facet_wrap(~drv, labeller = as_labeller(
    c(`4` = "4-Wheel", f = "Front", r = "Rear")
  )) +
  labs(title = "Vehicles by Manufacturer & Drive Type",
       x = "Count", y = NULL) +
  theme_uw(grid = "x") +
  theme(legend.position = "none")
```

### Continuous (light)

`scale_fill_uw_c()` and `scale_color_uw_c()` run from UW Light Gray to
Badger Red:

```{r scales-continuous}
ggplot(faithfuld, aes(waiting, eruptions, fill = density)) +
  geom_tile() +
  scale_fill_uw_c() +
  labs(title = "Old Faithful Eruption Density",
       x = "Waiting (min)", y = "Eruption (min)") +
  theme_uw(grid = "none")
```

---

## Dark theme

`theme_uw_dark()` is designed for slides and poster panels. Two styles are
available via the `style` argument.

### `style = "black"` (default)

Near-black background (`#121212`) with a Badger Red title — the most versatile
dark option.

```{r theme-dark-black}
ggplot(mpg, aes(x = displ, y = hwy, color = drv)) +
  geom_point(size = 2.5, alpha = 0.9) +
  scale_color_uw_dark(labels = c("4-wheel", "Front", "Rear")) +
  labs(
    title    = "Engine Displacement vs. Highway MPG",
    subtitle = "Motor Trend Car Road Tests",
    x        = "Displacement (L)",
    y        = "Highway MPG",
    color    = "Drive"
  ) +
  theme_uw_dark()
```

### `style = "red"`

Badger Red background (`#C5050C`) with white text — high-impact title slides
and poster headers.

```{r theme-dark-red, fig.height = 3.8}
mpg |>
  count(manufacturer) |>
  slice_max(n, n = 8) |>
  ggplot(aes(x = n, y = reorder(manufacturer, n))) +
  geom_col(fill = "white") +
  labs(title = "Top Manufacturers", x = "Count", y = NULL) +
  theme_uw_dark(style = "red", grid = "x")
```

### Continuous (dark)

`scale_fill_uw_dark_c()` runs Badger Red → White, suited to dark panels:

```{r scales-dark-continuous}
ggplot(faithfuld, aes(waiting, eruptions, fill = density)) +
  geom_tile() +
  scale_fill_uw_dark_c() +
  labs(title = "Old Faithful Eruption Density",
       x = "Waiting (min)", y = "Eruption (min)") +
  theme_uw_dark(grid = "none")
```

---

## Quarto templates

`use_uw_pdf()`, `use_uw_revealjs()`, and `use_uw_beamer()` copy starter
templates into any project directory. Run them once per project, then render
normally with `quarto render`.

```{r use-templates, eval = FALSE}
# PDF document (copies uw-brand.tex, _quarto.yml, template.qmd)
use_uw_pdf()

# RevealJS presentation (copies _uw-light.scss, _uw-dark.scss, template.qmd)
use_uw_revealjs()

# Beamer/PDF presentation (copies _uw-beamer-preamble.tex, title.tex, template.qmd)
use_uw_beamer()

# All three default to getwd(). Use path = to target a subdirectory.
use_uw_revealjs(path = "slides")

# Use overwrite = TRUE to refresh files from the package.
use_uw_pdf(overwrite = TRUE)
```

### File inventory

| Function | Files copied |
|---|---|
| `use_uw_pdf()` | `uw-brand.tex`, `_quarto.yml`, `template.qmd` |
| `use_uw_revealjs()` | `_uw-light.scss`, `_uw-dark.scss`, `template.qmd` |
| `use_uw_beamer()` | `_uw-beamer-preamble.tex`, `title.tex`, `template.qmd` |

---

## Switching light ↔ dark

The light and dark versions of each format are designed to be toggled with
minimal changes.

### RevealJS

In the YAML front matter, swap the theme line:

```yaml
# Light:
theme: [default, _uw-light.scss]

# Dark:
theme: [default, _uw-dark.scss]
```

In the setup chunk, match the plot theme:

```r
theme_set(theme_uw(base_size = 14))       # light
theme_set(theme_uw_dark(base_size = 14))  # dark
```

### Beamer

In `_uw-beamer-preamble.tex`, flip one line:

```latex
\uwdarkfalse   % light (default)
\uwdarktrue    % dark
```

Match the plot theme in the setup chunk (use `base_size = 9` for Beamer):

```r
theme_set(theme_uw(base_size = 9))       # light
theme_set(theme_uw_dark(base_size = 9))  # dark
```

### Consistent plot theming across a document

Set the theme once in a setup chunk so all subsequent plots inherit it:

```r
library(uwbranding)
theme_set(theme_uw())   # or theme_uw_dark()
```

Individual plots can still override with `+ theme_uw_dark(style = "red")` etc.
