---
title: "Presentation Title"
subtitle: "Subtitle or Course Name"
author: "Author Name"
institute: "University of Wisconsin–Madison"
date: today
date-format: "MMMM D, YYYY"

format:
  beamer:
    pdf-engine: xelatex
    include-in-header: _uw-beamer-preamble.tex
    aspectratio: 169
    fontsize: 11pt
    highlight-style: tango   # swap to 'zenburn' for dark mode
    template-partials:
      - title.tex

execute:
  echo: false
  warning: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(uwbranding)

# Match to the \uwdarkfalse / \uwdarktrue toggle in _uw-beamer-preamble.tex.
# Light (\uwdarkfalse):
theme_set(theme_uw(base_size = 9))
# Dark (\uwdarktrue) — uncomment and flip the preamble toggle:
# theme_set(theme_uw_dark(base_size = 9))
```

## Slide with bullet points

- First bullet point
- Second bullet point
  - Indented sub-point
- Third bullet point

\begin{uwbox}{Key concept}
Use \texttt{uwbox} from the preamble for brand-styled callouts.
\end{uwbox}

## Slide with a figure

```{r}
#| label: fig-scatter
#| fig-cap: "Caption appears below the figure."
#| fig-width: 5.5
#| fig-height: 3.2
#| out-width: "90%"

ggplot(mpg, aes(x = displ, y = hwy, color = drv)) +
  geom_point(size = 1.8, alpha = 0.85) +
  scale_color_uw(labels = c("4-wheel", "Front", "Rear")) +
  labs(
    title = "Displacement vs. Highway MPG",
    x     = "Displacement (L)",
    y     = "Highway MPG",
    color = "Drive"
  )
```

## Slide with two columns

:::::: {.columns}

::: {.column width="48%"}
Some explanatory text on the left.

- Point A
- Point B
:::

::: {.column width="48%"}
```{r}
#| fig-width: 3.5
#| fig-height: 3

mpg |>
  count(class) |>
  ggplot(aes(x = n, y = reorder(class, n))) +
  geom_col(fill = uw_color("badger_red")) +
  labs(x = "Count", y = NULL)
```
:::

::::::

## Incremental slide

Content appears item by item:

- First item \pause
- Second item \pause
- Third item

## {.plain}

\begin{center}
  {\Large\bfseries\color{BadgerRed} Thank You}\\[1em]
  {\normalsize Author Name}\\[0.3em]
  {\small Department $\cdot$ University of Wisconsin--Madison}\\[0.3em]
  {\small \texttt{author@wisc.edu}}
\end{center}
