---
title: ""
params:
  department: "Department of Example Studies"
  address: "1234 Example Street, Madison, WI 53706"
  email: "example@wisc.edu"
  website: "example.wisc.edu"

# Shared settings (pdf-engine, include-in-header, papersize, fontsize,
# colorlinks) come from _quarto.yml automatically.
format:
  pdf:
    documentclass: article
---

```{r}
#| label: setup
#| include: false

library(knitr)
```

```{r}
#| label: letterhead-fields
#| echo: false
#| results: asis

# Pushes the `params` set in the YAML front matter into the LaTeX
# commands defined in uw-letterhead.tex. Edit the `params:` block
# above (department, address, email, website) to customize the
# letterhead — no LaTeX editing required.
cat(sprintf("\\renewcommand{\\uwdepartment}{%s}\n", params$department))
cat(sprintf("\\renewcommand{\\uwaddress}{%s}\n", params$address))
cat(sprintf("\\renewcommand{\\uwemail}{%s}\n", params$email))
cat(sprintf("\\renewcommand{\\uwwebsite}{%s}\n", params$website))
```

\today

Recipient Name  
Recipient Title  
Recipient Address  

Dear Recipient Name,

Body of the letter goes here. Replace this paragraph — and the
salutation and closing above and below — with your own text. The
department, address, email, and website shown in the header/footer
are controlled entirely by the `params` block in the YAML front
matter, so this document can be reused across a lab or department by
changing only those four values.

Sincerely,

\vspace{3\baselineskip}

Sender Name  
Sender Title
