---
title: "Document Title"
subtitle: "Subtitle or Course Name"
author: "Author Name"
date: today
date-format: "MMMM D, YYYY"

# Shared settings (pdf-engine, include-in-header, papersize, fontsize,
# geometry, execute defaults) come from _quarto.yml automatically.
format:
  pdf:
    documentclass: article  # use 'report' for chapter-level headings
    toc: true
    toc-depth: 2
    number-sections: true

bibliography: references.bib  # remove if not using citations
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(uwbranding)

theme_set(theme_uw())
```

# Introduction {#sec-intro}

This document uses the UW–Madison brand identity: **Badger Red** headings,
*Crimson Pro* for body text, and Red Hat Display for headings and
sans-serif elements.

## Brand Colors Inline

Apply brand colors directly in LaTeX raw blocks:

`\badgerred{This text is Badger Red.}`{=latex}

`\darkred{This text is Dark Red.}`{=latex}

## Colored Boxes

```{=latex}
\begin{uwbox}[Key Concept]
Primary Badger Red callout box — good for definitions or key takeaways.
\end{uwbox}
```

```{=latex}
\begin{uwinfo}[Background]
Light gray info box — good for supplementary context.
\end{uwinfo}
```

# Figures {#sec-figures}

```{r}
#| label: fig-example
#| fig-cap: "A sample ggplot2 figure using UW brand colors."
#| fig-width: 5
#| fig-height: 3.5

tibble(
  group = c("A", "B", "C", "D"),
  value = c(42, 67, 31, 55)
) |>
  ggplot(aes(x = value, y = group, fill = group)) +
  geom_col() +
  scale_fill_uw(guide = "none") +
  labs(x = "Value", y = NULL)
```

# Tables {#sec-tables}

| Variable | Mean | SD |
|---|---|---|
| Height (cm) | 175.2 | 8.4 |
| Weight (kg) | 72.1 | 12.3 |

: Summary statistics. {#tbl-summary}

# Equations {#sec-equations}

$$
\bar{x} = \frac{1}{n} \sum_{i=1}^{n} x_i
$$ {#eq-mean}

# References {.unnumbered}

::: {#refs}
:::
