---
title: "Presentation Title"
subtitle: "Subtitle or Course Name"
author: "Author Name"
institute: "University of Wisconsin–Madison"
date: today
date-format: "MMMM D, YYYY"

format:
  revealjs:
    # Light: white background, Badger Red headings
    theme: [default, _uw-light.scss]
    # Dark: near-black background, Badger Red accents
    # theme: [default, _uw-dark.scss]

    slide-number: c/t
    progress: true
    width: 1280
    height: 720
    margin: 0.08
    highlight-style: github   # swap to 'github-dark' with dark theme
    code-line-numbers: false
    controls: false
    hash: true

execute:
  echo: false
  warning: false
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(uwbranding)

# Match to the theme: line above.
# Light (_uw-light.scss):
theme_set(theme_uw(base_size = 14))
# Dark (_uw-dark.scss) — uncomment and swap scss above:
# theme_set(theme_uw_dark(base_size = 14))
```

## Slide with bullet points

- First bullet point
- Second bullet point
  - Indented sub-point
- Third bullet point

## Slide with a figure

```{r}
#| label: fig-scatter
#| fig-width: 7
#| fig-height: 4.2

ggplot(mpg, aes(x = displ, y = hwy, color = drv)) +
  geom_point(size = 2.5, alpha = 0.85) +
  scale_color_uw(labels = c("4-wheel", "Front", "Rear")) +
  labs(
    title = "Engine Displacement vs. Highway MPG",
    x     = "Displacement (L)",
    y     = "Highway MPG",
    color = "Drive"
  )
```

## Slide with two columns

:::: {.columns}

::: {.column width="48%"}
Some explanatory text, a list, or another element.

- Point A
- Point B
:::

::: {.column width="48%"}
```{r}
#| fig-width: 5
#| fig-height: 4

mpg |>
  count(class) |>
  ggplot(aes(x = n, y = reorder(class, n))) +
  geom_col(fill = uw_color("badger_red")) +
  labs(x = "Count", y = NULL)
```
:::

::::

## Callout box

::: {.uw-box}
**Key takeaway** — Badger Red border box defined in `_uw-light.scss`.
:::

## Incremental reveal {.incremental}

- First revealed
- Then this one
- Finally this

## Speaker notes demo

Main slide content.

::: {.notes}
Press **S** to open speaker view. Notes don't appear on the main slide.
:::

## Section divider {background-color="#C5050C"}

::: {style="color: white; font-size: 1.6em; font-weight: bold;"}
Section Title
:::

## Thank you {background-color="#C5050C"}

::: {style="color: white; text-align: center;"}

**Author Name**

Department · University of Wisconsin–Madison

`author@wisc.edu`

:::
